Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-04-13 ltx/BrainIDE.tex
trying to fix stoopid conflict
small changes to paper

\documentclass[onecolumn,draftcls]{IEEEtran}

% \usepackage{graphicx}
\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
\usepackage{color}                    % For creating coloured text and background
\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
% TODO environment
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

% can use linebreaks \\ within to get better formatting as desired
\title{Estimation of Intracortical Connectivity in a Dynamical Neural Field Model}

@@

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}. In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

There are two options available to alleviate problems with aliasing. The first is to increase the spatial sampling frequency (using a higher resolution of sensors), and the second is to use wider sensors, which act like an anti-aliasing filters. The first option is more desirable, since more information is retained. If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gentle allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur. In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations. It may be estimated using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques. Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics. However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem~\cite{Sanner1992}. This is further illustrated our results.

@@

\section{Comparison of Estimated Parameters and True Parameters}

\begin{algorithm}
\caption{The Unscented Kalman Filter}\label{CPTEMDAlgorithm}
\begin{algorithmic}[1]
\State $k=1$
\State use CPT from Algorithm~\ref{CPTAlgorithm} to estimate $\phi_k(n)$ from $y(n)$
\State find local extrema of $cos\left(\phi_k(n)\right)$
\State use extrema to form the splines $s_{min,k}(n)$ and $s_{max,k}(n)$
\State calculate $x_{0,k}(n) = 0.5\left(s_{min,k}(n) + s_{max,k}(n)\right)$
\State find local maxima of $h_k(n)$
\State use maxima to form the spline $r_k(n) = s_{max,k}(n)$
\While { $x_{0,k}(n)$ is not monotonic }
    \State $k=k+1$
    \State perform CPT on $x_{0,k-1}(n)$ to estimate $\phi_{k}(n)$
    \State repeats steps 3 to 7 to approximate parameters
\EndWhile

\end{algorithmic}
\end{algorithm}

>>>>

\documentclass[onecolumn,draftcls]{IEEEtran}
%this is shit
% \usepackage{graphicx}
\usepackage{graphicx, algorithm, algorithmicx, algpseudocode}
\usepackage{color}                    % For creating coloured text and background
\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
% TODO environment
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

\title{Estimation of Intracortical Connectivity in a Dynamical Neural Field Model}

@@

Considering the spectral representation of the dynamic field at time $t$ denoted by $W_t(\boldsymbol{\nu})$ \todo{can this be $V_t(\boldsymbol{\nu})$}, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $W_t(\boldsymbol{\nu})$ need to be spatially bandlimited. Such a condition is usually satisfied due to the bandlimiting effect of most practical kernels and the spatially colored covariance functions \todo{~cite\{some eeg literature here\}}. In addition, the Gaussian pick-up of the sensors provides a low-pass filtering effect, further limiting the bandwidth of the field. Thus the spectral response $W_t(\boldsymbol{\nu})$ is usually band-limited with $W_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors needs to within $\frac{1}{2\nu_c}$. Satisfying this condition ensures that the hidden dynamic field $w_t(\mathbf{r})$ can be inferred from the sampled observation $\mathbf{y}(t)$.

There are two options available to alleviate problems with aliasing. The first is to increase the spatial sampling frequency (using a higher resolution of sensors), and the second is to use wider sensors, which act like an anti-aliasing filters. The first option is more desirable, since more information is retained. If sensors are modelled as having a Gaussian pickup range than the slope of the attenuation will be gradual allowing for some low amplitude high frequency components to still be present and mild aliasing will still occur. In practice, the bandwidth of the cortex can not be estimated by traditional electrophysiological measurements due to spatial limitations. It may be estimated using other modalities with higher spatial resolution such as, fMRI, NIRS or other optical imaging techniques. Errors associated with mild aliasing result in distortions in the high frequency components of the field dynamics. However, after applying the basis function decomposition, high frequency component contribute negligibly to the inverse problem and are therefore not a major problem~\cite{Sanner1992}. This is further illustrated our results.

@@

\section{Results}

\subsection{Frequency Analysis}
Figure~\ref{SprectralAnalysis} shows the spectra of the connectivity kernel, the disturbance covariance, the field filtered by the sensor kernel and the observations.

\subsection{State and Parameter Estimation}
